---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EncircleR

The goal of EncircleR is to automate and streamline circRNA analysis, by providing a graphical interface for selecting and downloading reference files, Perform read trimming and read mapping, and finally to perform circRNA detection by exploring backsplice junction contents.



### Dependencies

Install the latest version of R and R-studio

 * R (https://cran.rstudio.com/), Statistical programming language for running EncircleR
 * Rstudio (https://rstudio.com/products/rstudio/download/#download), Graphical R interface which simplifies executing and openning EncircleR.

Install the `circulaR` package from github, following its readme: https://github.com/KasperThystrup/circulaR
 

In order to install the `EncirclaR` R package, you must ensure to install
the following Biocodncutor packages:

 * AnnotationHub
 * S4Vectors
 * plyranges

```{r, eval = FALSE}
install.packages("BiocManager")
BiocManager::install(c("AnnotationHub", "S4Vectors", "plyranges"))
```

In addition, `devtools` r package must be installed, to enable easy
installation of `EncirclaR` from github.

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("https://github.com/KasperThystrup/EncircleR")
```

## Troubleshooting
This should install all dependencies from the official CRAN repository.
However, if something does not work out, try to install the CRAN
dependencies manually before running the install github command again:

 * logger
 * config
 * ggplot2
 * golem
 * shinyjs
 * shiny
 * processx
 * attempt
 * DT
 * glue
 * htmltools
 * shinydashboard
 * readr
 * tibble
 * tidyr
 * scales
 * stringr
 * dplyr

```{r, eval = FALSE}
install.packages(c("logger", "config", "ggplot2", "golem", "shinyjs", "shiny", "processx", "attempt", "DT", "glue", "htmltools", "shinydashboard", "readr", "tibble", "tidyr", "scales", "stringr", "dplyr", "circulaR"))
```

